Interval Probability for Fuzzy Quantum Theories

### 2016-06-18 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} First example...

\begin{example}{[}One-qubit quantum probability measure{]} Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(E)=\begin{cases}
1 & \textrm{, if }E=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
\mu_{\ket{0}}(E) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a probability measure. Because $\mu$ is almost
the same as a probability measure~$\tilde{\mu}_{\ket{0}}$, we only
need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
\]
On the other hand, $\mu$ cannot be induced by any mixed state because
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
\]
However, $\tilde{\mu}_{\rho}(E)=1$ if and only if $\rho$ represents
a pure state and $\rho=E$. \qed\end{example}

@@

\begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
Given a Hilbert space $\Hilb$ with the set of quantum events~$\events$,
a \emph{quantum interval-valued probability measure} is a function
$\mu:\events\rightarrow[0,1]$ such that:
\begin{itemize}
\item $\mu(\mathbb{0})=\left[0,0\right]$, 
\item $\mu(\mathbb{1})=\left[1,1\right]$, 
\item $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\mu\left(P\right)$,
and 
\item for mutually orthogonal projections $P_{i}$, we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\mu\left(P_{i}\right)$. 
\end{itemize}
\qed\end{definition}

@@

>>>>

\begin{example}[One-qubit quantum probability measure] Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(E)=\begin{cases}
1 & \textrm{, if }E=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
\mu_{\ket{0}}(E) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a probability measure. Because $\mu$ is almost
the same as a probability measure~$\tilde{\mu}_{\ket{0}}$, we only
need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
\]
On the other hand, $\mu$ cannot be induced by any mixed state because
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
\]
However, $\tilde{\mu}_{\rho}(E)=1$ if and only if $\rho$ represents
a pure state and $\rho=E$. \qed\end{example}

@@

\begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
Given a Hilbert space $\Hilb$ with the set of quantum events~$\events$,
and a collection of intervals~$\mathscr{I}$, a \emph{quantum $\mathscr{I}$-interval-valued
probability measure} is a function~$\mu:\events\rightarrow\mathscr{I}$
such that: 
\begin{itemize}
\item $\mu(\mathbb{0})=\left[0,0\right]$, 
\item $\mu(\mathbb{1})=\left[1,1\right]$, 
\item $\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\mu\left(P\right)$,
and 
\item for mutually orthogonal projections $P_{i}$, we have $\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\mu\left(P_{i}\right)$. 
\end{itemize}
\qed\end{definition}

@@

When we pick $\mathscr{I}=\left\{ \left[x,x\right]\middle|x\in\left[0,1\right]\right\} $,
for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
we can define a corresponding quantum \emph{$\mathscr{I}$}-interval-valued
probability measure~$\mu':\events\rightarrow\mathscr{I}$ by $\mu'\left(E\right)=\left[\mu\left(E\right),\mu\left(E\right)\right]$.
In this sense, every usual quantum probability measure can be considered
as a quantum interval-valued probability measure. There are more interesting
examples as we now show.
